### 2015-11-27 pfpl/cheatsheet.tex
First draft of chapter 1

\documentclass[12pt]{article}
\usepackage[margin=.5in]{geometry}
\begin{document}
\begin{tabular}[b] {p{.1\textwidth} p{.15\textwidth} p{.22\textwidth} p{.4\textwidth}}
Expression & Name & Say & Meaning \\ \\
$\mathcal{P}$ & Script P & Proposition & Something to be proved \\
$\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about abstract syntax tree $\it{a}$

\end{tabular}

>>>>

\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{proof}
\usepackage{hyperref}

\usepackage[margin=.5in]{geometry}
\begin{document}
\section*{Chapter 1}
\begin{tabular}[b] {p{.15\textwidth} p{.15\textwidth} p{.22\textwidth} p{.4\textwidth}}
Expression & Name & Say & Meaning \\ \\
$\mathcal{P}$ & Script P & Proposition & Something to be proved \\
$\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about abstract syntax tree $\it{a}$ \\
$\mathcal{O}$ & Script O & Operator & An operator that can be used in an AST \\
$\mathcal{O}(\it{a})$ & Script O of $\it{a}$ & Operator of arity $\it{a}$ & An operator of a given arity \\
$\mathcal{X}_{\it{s}}$ & Script X sub s & Variable $\it{x}$ of sort $\it{s}$ & A variable $\it{x}$ of sort $\it{s}$ \\
$\{ \it{X}_{s} \} _{\it{s} \in \mathcal{S}}$  & Family & Set $ \it{X} $ of s & a sort-indexed family of disjoint finite sets $ \it{X}_s $ of variables $\it{x}$ of sort $ \it{s} $ \\
$\left[ \it{b} / \it{x}\right] \it{a}$ & Substitution & Substitute $\it{b}$ for $\it{x}$ in $\it{a}$ & Substitute $\it{b}$ for $\it{x}$ in $\it{a}$ \\
$ \it{x}_1, ... ,\it{x}_{\it{n}}.\it{a} $ & Abstractor & Bind variables $\it{x_n}$ to expression $\it{a}$ & Bind variables $\it{x_n}$ to expression $\it{a}$ \\
$ \overrightarrow{\it{x}} $ & X arrow & List of $\it{x}s$ & $ \it{x}_1, ... ,\it{x}_{\it{n}} $ \\
$ \rho : \overrightarrow{\it{x}} \leftrightarrow \overrightarrow{\it{x}}'$ & Fresh renaming & Freshen $ \it{x} $ in $ \it{a} $ renaming & A bijection between $ \overrightarrow{\it{x}} $ and $ \overrightarrow{\it{x}}' $ where $ \overrightarrow{\it{x}}'$ is fresh for $\it{X}$ . \\
$\widehat{\rho}_i (a_i)$ & Rho hat sub i & Rename result & The result of applying the renaming $ \rho $ to $ \it{a} $ \\
$ =_\alpha $ & Equal alpha & $ \it{\alpha-equivalence} $ & Equal trees up to renaming \\
$ \overset{\Delta}{=} $ & & & \\
\end{tabular}
